Data Management for LSST Special Programs

### 2024-03-27 sec_intro.tex
consistency

This is a Rubin Data Management term to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.
Special Processing creates data products that are unique and separate from those produced
by standard processing for the Main Survey.

Special Processing is likely to use different inputs or configurations for the
LSST Science Pipelines, or to run on different timescales, than standard processing - 
as appropriate for the Special Programs' data and science goals.
However, the development and application of specialized \emph{algorithms} or new software
is beyond the scope of Special Processing.

Examples of Special Processing include the processing
of images with non-standard exposure times, images obtained
during twilight, or nightly stacking and differencing
of images in deep drilling fields.
See Section~\ref{ssec:proc_special} for more detailed examples of Special Processing.

@@

In some cases, standard processing is also appropriate for Special Programs.

@@

User-Generated Processing for Special Programs data would be necessary in cases where
the science goals require custom algorithms, software, or very large computational
capacities which are beyond the scope of Special Processing or the Rubin-provided
computational resources (Section~\ref{ssec:sci_comp}).

>>>>

This is a Rubin Data Management term to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.

Special Processing will only be done in certain cases when it
is determined, by Rubin Data Management, to be both "possible and necessary"
under the definitions provided in Section~\ref{ssec:sci_sproc}.

Special Processing is likely to use different inputs or configurations for the
LSST Science Pipelines, or to run on different timescales, than standard processing - 
as appropriate for the Special Programs' data and science goals.
Special Processing creates data products that are unique and separate from those produced
by standard processing for the Main Survey.
Examples of Special Processing include the processing
of images with non-standard exposure times, images obtained
during twilight, or nightly stacking and differencing
of images in deep drilling fields.
See Section~\ref{ssec:proc_special} for more detailed examples of Special Processing.

@@

In some cases, standard processing is also appropriate for Special Programs,
as discussed in Sections \ref{ssec:sci_pproc} and \ref{ssec:proc_reg}.

@@

User-Generated Processing for Special Programs data will be necessary in cases that
do not meet the conditions of "possible and necessary" as defined in
Section~ref\{ssec:sci_sproc} and further illustrated in Section~\ref{ssec:proc_special}.
This will include cases where the science goals require custom algorithms or software,
or computational capacities which are beyond the Rubin-provided
computational resources (Section~\ref{ssec:sci_comp}).
